experiment 1

### 2021-10-04 experiments/experiment 1/experiment-1.Rmd
Fix run_ss_var_experiment function to work with new parameter format and return consistent and reproducible results

```{r eval = FALSE}
visualise_temporal_env_eco()
```

@@

```{r eval = FALSE}

var_expt_res <- run_ss_var_experiment(parameter, var_expt[1:3,])

@@

Bring in various stable state datasets
```{r eval = FALSE}
## sim length 80'000, 20 x 20 factorial, reference maximum diversity
var_expt1 <- readRDS(here("experiments/experiment 1/data/ss_data_80000.RDS")) %>%
  mutate(sim_length = 80000) %>%
  mutate(ss_res = ss_by_a_N_result$result)

@@

## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
var_expt5 <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS")) %>%
  mutate(sim_length = 1000000)
stab_data5 <- var_expt5 %>%
  group_by(CB_var_gmax_s, CB_var_h_s,
           SB_var_gmax_s, SB_var_h_s,
           PB_var_gmax_s, PB_var_h_s, sim_length) %>%
  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
stab_data5 <- unnest(stab_data5, cols = c(stability_measures))
saveRDS(stab_data5, here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial.RDS"))

>>>>

```{r eval = FALSE}
visualise_temporal_env_eco(sim_res_novar3, sim_res_highvar3)
```

@@

```{r run_experiment, eval = eval_dynamics_flag}

var_expt_res <- run_ss_var_experiment(parameter, var_expt)

@@

Bring in various stable state datasets
```{r eval = FALSE}
## sim length 80'000, 20 x 20 factorial, reference maximum diversity

var_expt1 <- readRDS(here("experiments/experiment 1/data/ss_data_80000.RDS")) %>%
  mutate(sim_length = 80000)

@@

## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
var_expt5 <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS")) %>%
  mutate(sim_length = 1000000)
stab_data5 <- var_expt5 %>%
  group_by(CB_var_gmax_s, CB_var_h_s,
           SB_var_gmax_s, SB_var_h_s,
           PB_var_gmax_s, PB_var_h_s, sim_length) %>%
  do(stability_measures = get_stability_measures(.$ss_res[[1]]))
stab_data5 <- unnest(stab_data5, cols = c(stability_measures))
saveRDS(stab_data5, here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial.RDS"))
```
